---
title: 'Cleaning Master Dataset: All Surveys'
author: "Juan Ospina"
date: "11/1/2018"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
---

```{r clean system, message=TRUE, warning=TRUE, include=FALSE}
rm(list = ls()) # clean environment
```

```{r global options, echo=FALSE}
knitr::opts_chunk$set(
  # fig.path = 'figs/', fig.show = 'asis', dpi = 300, 
  # include = FALSE, 
  echo = FALSE, # run the code, show me only the graphs
  warning = FALSE, message = FALSE, cache = FALSE)
```

```{r packages}
library(magrittr)
library(Hmisc)
library(RColorBrewer)
library(reshape2)
# library(MASS) # negative binomial models
library(tidyverse)
library(emmeans) # to get adjusted means and to plot the summary statistics of models
library(kableExtra)
library(psych)
```

```{r}
d0 <- read_rds("../Newest Data/FIntv_2017_Comprehensive_withY1SpGradeData_withSYFUSNoT7_Cleaned.rds")
```


```{r}
source("../../../premat_intervention_jo/Research Assistants/scripts/custom_functions.R")
```


# Review Demographics

```{r}
# demographics <- c("race", "gend")
# 
# map2_chr(
#   .x = d0, 
#   .y = demographics, 
#   .f = check_vars_by_keywords
#   )
```

## Race

These are all the variables that have the keyword "race":

```{r}
race <- c("race")
check_vars_by_keywords(d0, race)
```

The variable *race* is the factor variable created from the numeric variable *race_nointl_wPI_USETHIS*. *race_intlfirst_wPI* includes International students.

Labels from *race_nointl_wPI_USETHIS*:

```{r}
attr(d0$race_nointl_wPI_USETHIS, "labels")
```

Labels from *race_intlfirst_wPI*:

```{r}
attr(d0$race_intlfirst_wPI, "labels")
```

Number of participants by race:

```{r}
demogs <- quos(race_nointl_wPI_USETHIS, race_intlfirst_wPI, race)

d0 %>% 
  # filter(!is.na(race_nointl_wPI_USETHIS)) %>% 
  demographics_pct(demogs)
```

## Gender

These are all the variables that have the keyword "gend":

```{r}
gender <- c("gend")
check_vars_by_keywords(d0, gender)
```

The variable *gend* is the factor variable created from the character variable *iGender*.

Labels from *iGender*:

```{r}
attr(d0$iGender, "labels")
```

Number of participants by gender:

```{r}
demogs <- quos(iGender, gend)

d0 %>% 
  # filter(!is.na(race_nointl_wPI_USETHIS)) %>% 
  demographics_pct(demogs)
```

## Social Class

These are all the variables that have the keyword "ses":

```{r}
ses <- c("ses")
check_vars_by_keywords(d0, ses)
# social <- c("status")
# check_vars_by_keywords(d0, social)
```

The variable *ses* is the factor variable created from the numeric variable *t1ses*. *ses_working_lowmiddle* is the factor variable created from the numeric variable *t1ses_workinglowermiddleclass*.

Labels of *t1ses*:

```{r}
attr(d0$t1ses, "labels")
```

Number of participants by SES:

```{r}
d0 %<>% 
  mutate(ses = 
           factor(t1ses, labels = c("working", "low-middle", "middle", "upper-middle", "upper")),
         ses_working_lowmiddle = 
           factor(t1ses_workinglowermiddleclass, labels = c("middle-to-upper", "working-to-low-middle"))
         )

demogs <- quos(t1ses, ses, ses_working_lowmiddle, t1ses_workinglowermiddleclass)

d0 %>% 
  # filter(!is.na(race_nointl_wPI_USETHIS)) %>% 
  demographics_pct(demogs)
```

## High School Status

These are all the variables that have the keyword "hs":

```{r}
hs <- c("hs")
check_vars_by_keywords(d0, hs)
```

The variable *hs_advantage* is the factor variable created from the numeric variable *t1hsadvantage*. *ses_working_lowmiddle* is the factor variable created from the numeric variable *t1ses_workinglowermiddleclass*.

Labels of *t1hsadvantage*:

```{r}
attr(d0$t1hsadvantage, "labels")
```

Number of participants by High School Status:

```{r}
d0 %<>% 
  mutate(hs_advantage = 
           factor(t1hsadvantage, labels = c("adv hs", "neither adv nor disadv", "disadv hs"))
         )

demogs <- quos(t1hsadvantage, hs_advantage)

d0 %>% 
  # filter(!is.na(t1hsadvantage)) %>% 
  demographics_pct(demogs)
```

## Parent Education

These are all the variables that have the keyword "edu":

```{r}
check_vars_by_keywords(d0, c("edu"))
```

*     *mother_edu* is the factor variable created from the numeric variable *t1mothereduc*. 
*     *father_edu* is the factor variable created from the numeric variable *t1fathereduc*.

Labels of *t1mothereduc* (*t1fathereduc* has the same):

```{r}
attr(d0$t1mothereduc, "labels")
```

Number of participants by Parent Education:

```{r}
mother_edu <- c("less than hs", "hs grad", "some college", "associate", 
                "bachelor", "some graduate", "master", "law", "medical", "doctoral", "don't know")

father_edu <- c("less than hs", "hs grad", "some college", "associate", 
                "bachelor", "some graduate", "master", "law", "medical", "doctoral", "don't know", "don't apply")

d0 %<>% 
  mutate(mother_edu = factor(t1mothereduc, labels = mother_edu),
         father_edu = factor(t1fathereduc, labels = father_edu),
         )

demogs <- quos(mother_edu, t1mothereduc)

d0 %>% 
  # filter(!is.na(mother_edu)) %>% 
  demographics_pct(demogs)

demogs <- quos(father_edu, t1fathereduc)

d0 %>% 
  # filter(!is.na(father_edu)) %>% 
  demographics_pct(demogs)
```

## First-Generation Status

These are all the variables that have the keyword "firstgen":

```{r}
check_vars_by_keywords(d0, c("firstgen"))
```

*     *firstgen* is the factor variable created from the numeric variable *firstgen_reg_USETHIS*. 

Labels of *firstgen_reg_USETHIS*:

```{r}
attr(d0$firstgen_reg_USETHIS, "labels")
```

Number of participants by First-Generation Status:

```{r}
demogs <- quos(firstgen, firstgen_reg_USETHIS)

d0 %>% 
  # filter(!is.na(firstgen)) %>% 
  demographics_pct(demogs)
```


# Export dataset with cleaned demographics

```{r}
d0 %>% 
  write_rds("../Newest Data/FIntv_2017_Comprehensive_withY1SpGradeData_withSYFUSNoT7_Cleaned_Demogs.rds")

d0 %>% 
  write_csv("../Newest Data/FIntv_2017_Comprehensive_withY1SpGradeData_withSYFUSNoT7_Cleaned_Demogs.csv")
```


```{r}
# d0 %>% count(t1condition, t1condition_Numeric)
```


