---
title: "Clean Pre-Matriculation Intervention Survey in Master Dataset"
author: "Juan Ospina"
date: "11/2/2018"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
---

```{r clean system, message=TRUE, warning=TRUE, include=FALSE}
rm(list = ls()) # clean environment
```

```{r global options, echo=FALSE}
knitr::opts_chunk$set(
  # fig.path = 'figs/', fig.show = 'asis', dpi = 300, 
  # include = FALSE, 
  echo = FALSE, # run the code, show me only the graphs
  warning = FALSE, message = FALSE, cache = FALSE)
```

```{r packages}
library(magrittr)
library(Hmisc)
library(RColorBrewer)
library(reshape2)
# library(MASS) # negative binomial models
library(tidyverse)
library(emmeans) # to get adjusted means and to plot the summary statistics of models
library(kableExtra)
library(psych)
```

```{r}
d0 <- read_rds("../Newest Data/FIntv_2017_Comprehensive_withY1SpGradeData_withSYFUSNoT7_Cleaned_Demogs.rds")
```

```{r load custom functions}
source("../../../premat_intervention_jo/Research Assistants/scripts/custom_functions.R")
```

# Pre-measures before receiving pre-matriculation intervention

## Independent reasons

Review variables with keyword "reason":

```{r}
check_vars_by_keywords(d0, c("reason"))
```

Items and scales:

*     *t1preReasons_independent*:

```{r}
attr(d0$t1preReasons_independent, "label")
attr(d0$t1preReasons_independent, "labels")
```

*     *t1preReasons_myinterest*:

```{r}
attr(d0$t1preReasons_myinterest, "label")
attr(d0$t1preReasons_myinterest, "labels")
```

*     *t1preReasonsIndepcomp2*:

```{r}
attr(d0$t1preReasonsIndepcomp2, "label")
```


**Correlations**:

```{r}
corr_table_p(d0, quos(t1preReasonsIndepcomp2, t1preReasons_independent,  t1preReasons_myinterest))
```

## Interdependent reasons

Items and scales:

*     *t1preReasons_familyproud*:

```{r}
attr(d0$t1preReasons_familyproud, "label")
attr(d0$t1preReasons_familyproud, "labels")
```

*     *t1preReasons_community*:

```{r}
attr(d0$t1preReasons_community, "label")
attr(d0$t1preReasons_community, "labels")
```

*     *t1preReasonsInterdepcomp2*:

```{r}
attr(d0$t1preReasonsInterdepcomp2, "label")
```


**Correlations**:

```{r}
corr_table_p(d0, quos(t1preReasonsInterdepcomp2, t1preReasons_familyproud, t1preReasons_community))
```

# Immediate DVs

## Independent qualities

Review variables with keyword "opport":

```{r}
check_vars_by_keywords(d0, c("qualities"))

check_vars_by_keywords(d0, c("reas"))
```

Items and scales:

*     *qualities_indownpath*:

```{r}
attr(d0$qualities_indownpath, "label")
attr(d0$qualities_indownpath, "labels")
```

*     *t1opportunty_becomeindepthinker4*:

```{r}
attr(d0$t1opportunty_becomeindepthinker4, "label")
attr(d0$t1opportunty_becomeindepthinker4, "labels")
```

*     *t1opportunty_independent_comp2*:

```{r}
attr(d0$t1opportunty_independent_comp2, "label")
```

**Correlations**:

```{r}
corr_table_p(d0, quos(t1opportunty_independent_comp2, t1opportunty_exploreinterests3,  t1opportunty_becomeindepthinker4))
```

## Interdependent opportunities

Items and scales:

*     *t1opportunty_joincommunities1R*:

```{r}
attr(d0$t1opportunty_joincommunities1R, "label")
attr(d0$t1opportunty_joincommunities1R, "labels")
```

*     *t1opportunty_giveback2R*:

```{r}
attr(d0$t1opportunty_giveback2R, "label")
attr(d0$t1opportunty_giveback2R, "labels")
```

*     *t1opportunty_interdependent_comp2*:

```{r}
attr(d0$t1opportunty_interdependent_comp2, "label")
```

**Correlations**:

```{r}
corr_table_p(d0, quos(t1opportunty_interdependent_comp2, t1opportunty_joincommunities1R,  t1opportunty_giveback2R))
```

## Friends attend university next year

*     *t1friendsgoingtoSU*:

```{r}
# check_vars_by_keywords(d0, c("friend"))
attr(d0$t1friendsgoingtoSU, "label")
attr(d0$t1friendsgoingtoSU, "labels")
```
