---
title: "Analyse C2017 Spring Survey"
author: "Juan Ospina"
date: "7/5/2018"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
---

```{r clean system, message=TRUE, warning=TRUE, include=FALSE}
rm(list = ls()) # clean environment
```

```{r global options, echo=FALSE}
knitr::opts_chunk$set(
  # fig.path = 'figs/', fig.show = 'asis', dpi = 300, 
  # include = FALSE, 
  echo = FALSE, # run the code, show me only the graphs
  warning = FALSE, message = FALSE, cache = FALSE)
```

```{r packages}
library(magrittr)
library(Hmisc)
library(RColorBrewer)
library(reshape2)
# library(MASS) # negative binomial models
library(tidyverse)
library(emmeans) # to get adjusted means and to plot the summary statistics of models
library(kableExtra)
library(psych)
```

```{r}
d.an <- read_rds("../Newest Data/FIntv_2017_Comprehensive_withY1SpGradeData_withSYFUSNoT7_Filtered.rds") 
```

```{r custom functions}
# sum_stats_round <- function(data, factors, variables) {
#   data %>% 
#     group_by(!!!factors) %>% 
#     summarise(
#       mean = round(mean(!!!variables, na.rm = TRUE), 2),
#       sd = round(sd(!!!variables, na.rm = TRUE), 2))
# }

n_obs <- function(x) sum(!is.na(x))
mn <- function(x) round(mean(x, na.rm = TRUE), 2)
mdn <- function(x) median(x, na.rm = TRUE)
std <- function(x) round(sd(x, na.rm = TRUE), 2)
lb <- function(x) round(mean(x, na.rm = TRUE) - sd(x, na.rm = TRUE), 2)
ub <- function(x) round(mean(x, na.rm = TRUE) + sd(x, na.rm = TRUE), 2)

sum_stats_round <- function(data, factors, variables) {
  data %>% 
    group_by(!!!factors) %>% 
    summarise(
      n = n_obs(!!!variables),
      mean = mn(!!!variables),
      median = mdn(!!!variables),
      sd = std(!!!variables),
      lower = lb(!!!variables),
      upper = ub(!!!variables))
}

sum_stats_round_new <- function(data, factors, variables) {
  ftr <- enquo(factors)
  var <- enquo(variables)
  
  data %>% 
    group_by(!!!ftr) %>% 
    summarise(
      n = n_obs(!!!var),
      mean = mn(!!!var),
      median = mdn(!!!var),
      sd = std(!!!var),
      lower = lb(!!!var),
      upper = ub(!!!var))
}

sum_stats_round_new2 <- function(data, factor1, factor2, variable) {
  ftr1 <- enquo(factor1)
  ftr2 <- enquo(factor2)
  var <- enquo(variable)
  
  data %>% 
    group_by(!!!ftr1, !!!ftr2) %>% 
    summarise(
      n = n_obs(!!!var),
      mean = mn(!!!var),
      median = mdn(!!!var),
      sd = std(!!!var),
      lower = lb(!!!var),
      upper = ub(!!!var))
}

geom_flat_violin <-
  function(mapping = NULL,
           data = NULL,
           stat = "ydensity",
           position = "dodge",
           trim = TRUE,
           scale = "area",
           show.legend = NA,
           inherit.aes = TRUE,
           ...) {
    ggplot2::layer(
      data = data,
      mapping = mapping,
      stat = stat,
      geom = GeomFlatViolin,
      position = position,
      show.legend = show.legend,
      inherit.aes = inherit.aes,
      params = list(trim = trim,
                    scale = scale,
                    ...)
    )
  }

GeomFlatViolin <-
  ggproto(
    "GeomFlatViolin",
    Geom,
    setup_data = function(data, params) {
      data$width <- data$width %||%
        params$width %||% (resolution(data$x, FALSE) * 0.9)
      
      # ymin, ymax, xmin, and xmax define the bounding rectangle for each group
      data %>%
        dplyr::group_by(.data = ., group) %>%
        dplyr::mutate(
          .data = .,
          ymin = min(y),
          ymax = max(y),
          xmin = x,
          xmax = x + width / 2
        )
    },
    
    draw_group = function(data, panel_scales, coord)
    {
      # Find the points for the line to go all the way around
      data <- base::transform(data,
                              xminv = x,
                              xmaxv = x + violinwidth * (xmax - x))
      
      # Make sure it's sorted properly to draw the outline
      newdata <-
        base::rbind(
          dplyr::arrange(.data = base::transform(data, x = xminv), y),
          dplyr::arrange(.data = base::transform(data, x = xmaxv), -y)
        )
      
      # Close the polygon: set first and last point the same
      # Needed for coord_polar and such
      newdata <- rbind(newdata, newdata[1,])
      
      ggplot2:::ggname("geom_flat_violin",
                       GeomPolygon$draw_panel(newdata, panel_scales, coord))
    },
    
    draw_key = draw_key_polygon,
    
    default_aes = ggplot2::aes(
      weight = 1,
      colour = "grey20",
      fill = "white",
      size = 0.5,
      alpha = NA,
      linetype = "solid"
    ),
    
    required_aes = c("x", "y")
  )
```

```{r raincloud plots custom functions}
plot_raincloud <- function(data, factor, variable) {
  ftr <- enquo(factor)
  var <- enquo(variable)
  
  data %>% 
    ggplot(aes_(y = var, x = ftr, fill = ftr)) +
    raincloud_violin +
    geom_point(aes_(y = var, color = ftr), 
               position = position_jitter(width = .15), size = .5, alpha = 0.8) +
    stat_summary_se + raincloud_boxplot + raincloud_guides + raincloud_theme_light + raincloud_theme +
    labs(x = "Condition", fill = "Condition")
}

# Example:
# d %>% 
# ggplot(aes(y = healthmosoverall_comp5, x = treat, fill = treat)) +
#   raincloud_violin +
#   geom_point(aes(y = healthmosoverall_comp5, color = treat), 
#              position = position_jitter(width = .15), size = .5, alpha = 0.8) +
#   geom_point(data = sum_stats_healthmosoverall_comp5_treat, aes(x = treat, y = mean),
#              position = position_nudge(x = 0.3), size = 1.5) +
#   stat_summary_se + raincloud_boxplot + raincloud_guides + raincloud_theme_light + raincloud_theme +
#   facet_grid(~ disadv) +
#   labs(x = "Condition", y = "Overall physical health", fill = "Condition")


raincloud_point <- function(data, factor, mn) {
  ftr <- enquo(factor)
  mn <- enquo(mn)
  
geom_point(data = data, aes_(x = ftr, y = mn), 
             position = position_nudge(x = 0.3), size = 1.5)
}

raincloud_theme <- 
  theme(text = element_text(size = 10),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, vjust = 0),
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.position = "right",
        plot.title = element_text(lineheight = .8, face = "bold", size = 16),
        panel.border = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.line.x = element_line(colour = 'black', size = 0.5, linetype = 'solid'),
        axis.line.y = element_line(colour = 'black', size = 0.5, linetype = 'solid'),
        strip.text = element_text(color = "Black"), strip.background = element_blank())

raincloud_boxplot <-
  geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5)

raincloud_guides <- 
  guides(fill = FALSE, color = FALSE)
  
raincloud_theme_light <- 
  theme_light()

raincloud_violin <- 
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8)

stat_summary_se <- 
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1, position = position_nudge(x = .3, y = 0))
```

```{r bar plot settings}
# These elements are not going to change from plot to plot, so I added them here so we don't have to copy paste unnecesary code
pd1 <- position_dodge()
pd2 <- position_dodge(0.1)
pd3 <- position_dodge(width = 0.9)
black1 <- element_text(color = "White")
black2 <- element_rect(fill = "black", colour = "Black", size = NULL, linetype = NULL, color = "Black", inherit.blank = FALSE)

theme <- theme(strip.text = black1, strip.background = black2, axis.text = element_text(size = 14),
        axis.title = element_text(size = 14), strip.text.x = element_text(size = 14, colour = "white"), # "colour" changes the color of the facets
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())

theme.cond <- theme(strip.text = black1, strip.background = black2, axis.text = element_text(size = 11),
        axis.title = element_text(size = 14), strip.text.x = element_text(size = 14, colour = "white"),
         panel.grid.major = element_blank(), panel.grid.minor = element_blank())

theme1 <- theme_light()
# theme1 <- theme_classic()
# theme1 <- theme_linedraw()
# theme1 <- theme_minimal()
# theme1 <- theme_void()

guides_no <- guides(fill = FALSE)
pd4 <- position_stack(vjust = 1.1)

color_cd_purp <- scale_fill_manual("legend", values = c("ctl" = "salmon", "purp" = "#56B4E9"))

color_treat <- scale_fill_manual("legend", values = c("ctl" = "salmon", "treat" = "#56B4E9")) # add only to graphs between treatment and control

positions_treat <- c("ctl", "treat")
labels_treat <- scale_x_discrete(labels = c('Control','Treatment'), limits = positions_treat)

positions_cd_purp <- c("ctl", "purp")
labels_cd_purp <- scale_x_discrete(labels = c('Control','Purpose'), limits = positions_cd_purp)

positions_cond <- c("ctl", "bel", "cul", "wf")

labels_cond <- scale_x_discrete(labels = c('Control', 'Belonging','Culture', 'Wise\nFeedback'), limits = positions_cond)

color_cond <- scale_fill_manual("legend", values = c("ctl" = "#F8766D", "bel" = "#7CAE00", "cul" = "#00BFC4", "wf" = "#C77CFF"))

adv_names <- 
  c('adv'="Advantaged",
    'disadv'="Disadvantaged")

gend_names <- 
  c('m'="Male",
    'f'="Female")

# Scales
scale_y_4 <- scale_y_continuous(breaks = seq(1, 4, 1))
scale_y_5 <- scale_y_continuous(breaks = seq(1, 5, 1))
scale_y_7 <- scale_y_continuous(breaks = seq(1, 7, 1))
scale_y_10 <- scale_y_continuous(breaks = seq(1, 10, 1))
scale_y_100 <- scale_y_continuous(breaks = seq(1, 100, 20))
scale_y_50 <- scale_y_continuous(breaks = seq(1, 50, 10))
scale_y_z <- scale_y_continuous(breaks = seq(-1, 1, 0.25))

coord_cartesian_4 <- coord_cartesian(ylim = c(0, 4))
coord_cartesian_5 <- coord_cartesian(ylim = c(1, 5))
coord_cartesian_7 <- coord_cartesian(ylim = c(1, 7))
coord_cartesian_10 <- coord_cartesian(ylim = c(1, 10))
coord_cartesian_z <- coord_cartesian(ylim = c(-1, 1))

mean_round3 <- geom_text(aes(label = format(emmean, digits = 3), y = 1))
mean_round_gpa <- geom_text(aes(label = format(emmean, digits = 3), y = .2))
mean_roundz <- geom_text(aes(label = format(emmean, digits = 2), y = -.5))

error_bar <- geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = .2, position = pd2)
```

```{r bar plot functions }
plot_bar_x_y <- function(data = data, x_var = x_var, x_labels = x_labels, x_color = x_color,
                               y_var = y_var, labs_y = labs_y,
                               scale = scale, coord_cartesian = coord_cartesian, mean_round = mean_round) {
x_var <- enquo(x_var)
y_var <- enquo(y_var)

data %>%
  ggplot(aes(x = !!x_var, y = !!y_var, fill = !!x_var, group = !!x_var)) +
  geom_bar(position = pd1, stat = "identity") + error_bar + theme1 + theme + guides_no + mean_round +
  coord_cartesian + scale + # this is where you change the scale
  x_labels + x_color + labs_y
}

# plot_bar_x_y(data = sum_stats, x_var = cd_purp_ec, x_labels = labels_cd_purp, 
#                    x_color = color_cd_purp,
#                    y_var = emmean, labs_y = labs(x = "", y = "Belonging at College"),
#                    scale = scale_y_7, coord_cartesian = coord_cartesian_7, mean_round = mean_round3)

# Example:
# You can use this code as long as you get the sum_stats of any model by any two catgorical variables (e.g. condition and disadvantaged status or condition and gender, or condition and race) by condition and disadvatanged status
# plot_bar_purp_gend(sum_stats, scale_y_7, coord_cartesian_7, mean_round3) +
#  labs(x = "", y = "Belonging at College")

# General function version:
# Need to specify more stuff but it's more general so you can use it with more grouping variables
plot_bar_x_y_group <- function(data = data, x_var = x_var, x_labels = x_labels, x_color = x_color,
                               y_var = y_var, labs_y = labs_y,
                               group_var = group_var, group_names = group_names,
                               scale = scale, coord_cartesian = coord_cartesian, mean_round = mean_round) {
x_var <- enquo(x_var)
y_var <- enquo(y_var)
group_var <- enquo(group_var)

data %>%
  ggplot(aes(x = !!x_var, y = !!y_var, fill = !!x_var, group = !!x_var)) +
  geom_bar(position = pd1, stat = "identity") + error_bar + theme1 + theme + guides_no + mean_round +
  coord_cartesian + scale + # this is where you change the scale
  facet_grid(, vars(!!group_var), labeller = as_labeller(group_names)) + # ignore warning, this is to make the plot facet the variables in the way that we want it
  x_labels + x_color + labs_y
}

# Working example if you add this below the summary(model) of belonging at college
# plot_bar_x_y_group(data = sum_stats, x_var = treat_ec, x_labels = labels_treat, x_color = color_treat,
#                    y_var = emmean, labs_y = labs_purpose,
#                    group_var = disadv_ec, group_names = adv_names,
#                    scale = scale_y_5, coord_cartesian = coord_cartesian_5, mean_round = mean_round3)

# Working function with mtcars
plot_x_y_factor <- function(data = data, x_var = x_var, y_var = y_var, group_var = group_var){
x_var <- enquo(x_var)
y_var <- enquo(y_var)
group_var <- enquo(group_var)

ggplot(data, aes(!!x_var, !!y_var)) + 
  geom_point() + 
  facet_wrap(vars(!!group_var))
}

plot_x_y_factor(data = mtcars, wt, mpg, cyl)
```


```{r custom functions describe sample}
table.describe <- function(data, vector){
  data %>% select(!!!vector) %>% describe %>% round(., digits = 2) %>% kable 
}
```

```{r}
t4 <- d.an %>% select(t4belongcomp8:t4integration_CF_ASS_EI_Mentor)

# d.an %>% filter(t4ResponseID != "")
```

# Effect sizes

## Is there inequality?

We want to focus on the effect sizes between males and females in the control group.

### Inequalities between males and females in control

Effect sizes (Cohen's *d*) between males and females in control:

```{r}
d.an %>% count(cd_purp, cd_purp_num) %>% select(-n)

vars_cont <- quos(purpose_comp2, happy_comp4, belong_comp6, lifesat, happy_comp4, healthmosoverall_comp5, stressdaily, pss_comp4, overallmentalhealth_comp5_z, Y1_Sp_CumGPA, activism_z_comp2, activism_engaged, activism_hours_use_this, job_applylearning, honors_yes_use_this, perf_highexpect, perf_notsat_comp2, collexp_comp4, qualitiesind_comp2, qualitiesinter_comp4, potsuc_comp2, potential_use_this, success_use_this, mentor_yes)

cohend_ineq <- cohen.d.by(x = d.an %>% select(cd_purp_num, gend_num, !!!vars_cont), group = "gend_num", group2 = "cd_purp_num", alpha = .05) %>% summary

cohend_ineq %<>% 
  rownames_to_column() %>% 
  filter(rowname == "gend_numforcd_purp_num0") %>% 
  select(-rowname) %>% 
  round(., digits = 2)

cohend_ineq
```

## Is there a treatment effect?

### Differences between control and purpose for all students

```{r}
cohend_cd_purp_all <- cohen.d(d.an %>% select(cd_purp_num, !!!vars_cont), group = "cd_purp_num", alpha = .05)

cohend_cd_purp_all <- cohend_cd_purp_all$cohen.d

cohend_cd_purp_all %<>% as.data.frame() %>% rownames_to_column()

cohend_cd_purp_all
```

### Differences between control and any cd_purpment for males and females

Effect sizes (Cohen's *d*) between control and any cd_purpment for advantaged and disadvantaged students:

```{r}
d.an %>% count(gend, gend_num) %>% select(-n)

cohend_cd_purp_gend <- cohen.d.by(x = d.an %>% select(cd_purp_num, gend_num, !!!vars_cont), group = "cd_purp_num", group2 = "gend_num", alpha = .05) %>% summary

cohend_cd_purp_gend %<>% 
  rownames_to_column() %>% 
  mutate_at(vars(-c(rowname)), funs(round(., 2))) %>% 
  mutate(gender = ifelse(rowname == "cd_purp_numforgend_num0", "male", "female"))
  # filter(rowname == "cd_purp_numforgend_num1") %>% 
  # select(-rowname) %>%
  # round(., digits = 2)

cohend_cd_purp_gend
```

# Spring Survey (t4) 
## Descriptive tables
```{r}
var_list <- quos(t4belongcomp8, t4BUcomp2, t4happycomp2, t4stresscomp2, t4lonelycomp, t4transitioncomp3,
                 t4futureselvescomp5, t4abilitycomp2,
  t4acanxietycomp3, t4feedbackcomp2, t4percievedsocsuppcomp3,
  t4friendsnumber_mis, t4friendsnumber_0, t4friendsclose_sum,
  t4friendsclose_ave, t4friendsdensecomp2, t4dormcomp2, t4sucbehvcomp6,
  t4indepcomp4, t4interdepcomp4, t4purpose_prosocialcomp3,
  t4purposeindepcomp7, t4healthcomp5, t4Gstreothrtcomp3,
  t4Rstreothrtcomp3, t4meaningcomp3)
```

### Purpose vs Control

```{r}
d.an %>% select(!!!var_list) %>% describeBy(d.an$cd_purp)
```

### By Disadvantaged Status
```{r}
d.an %>% select(!!!var_list) %>% describeBy(d.an$disadv)
```

### By Treatment and Disadvantaged Status
```{r}
d.an %>% select(!!!var_list) %>% describeBy(d.an %>% select(treat, disadv))
```

### By Each Condition and Disadvantaged Status
```{r}
d.an %>% select(!!!var_list) %>% describeBy(d.an %>% select(cond, disadv))
```

## Analyses
### Belonging at College (t4)
#### Collapsed Treatments

Plot without covariates:
```{r}
model <- lm(t4belongcomp8 ~ treat * disadv, data = d.an)

sum_stats <- emmeans(model, ~ treat | disadv) %>% as.tibble()
sum_stats %>% mutate_at(vars(-c(treat, disadv)), funs(round(., 2))) %>%  kable()

sum_stats %>%
  ggplot(aes(x = treat, y = emmean, fill = treat, group = treat)) +
  geom_bar(position = pd1, stat = "identity") +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = .2, position = pd2) +
  theme1 + theme + guides_no + labels_treat +
  geom_text(aes(label = format(emmean, digits = 3), y = 1)) +
  coord_cartesian(ylim = c(1, 7)) + # this is where you change the scale
    labs(x = "", y = "Belonging at College") +
  facet_grid(~ disadv, labeller = as_labeller(adv_names))

summary(model)
```

#### Any Condition

Plot without covariates:
```{r}
model <- lm(t4belongcomp8 ~ cond * disadv, data = d.an)

sum_stats <- emmeans(model, ~ cond | disadv) %>% as.tibble()
sum_stats %>% mutate_at(vars(-c(cond, disadv)), funs(round(., 2))) %>%  kable()

sum_stats %>%
  ggplot(aes(x = cond, y = emmean, fill = cond, group = cond)) +
  geom_bar(position = pd1, stat = "identity") +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = .2, position = pd2) +
  theme1 + theme.cond + guides_no + labels_cond +
  geom_text(aes(label = format(emmean, digits = 3), y = 1)) +
  coord_cartesian(ylim = c(1, 7)) + # this is where you change the scale
    labs(x = "", y = "Belonging") +
  facet_grid(~ disadv, labeller = as_labeller(adv_names))

summary(model)
```
