---
title: "Reliability Ospina SPSP Poster"
author: "Juan Ospina"
date: "1/31/2019"
output: html_document
---

```{r clean system, message=TRUE, warning=TRUE, include=FALSE}
rm(list = ls()) # clean environment
```

```{r global options, echo=FALSE}
knitr::opts_chunk$set(
  # fig.path = '../plots/', fig.show = 'asis', dev = 'pdf',
  dpi = 150, 
  # include = FALSE, 
  echo = FALSE, # run the code, show me only the graphs
  warning = FALSE, message = FALSE, cache = FALSE)
```

```{r packages}
# install.packages(c("RColorBrewer", "reshape2", "tidyverse"))
library(haven) # package to import SPSS files in R. Useful to import SPSS files and export them as csv
library(magrittr)
library(Hmisc)
# library(RColorBrewer)
library(reshape2)
library(tidyverse)
library(kableExtra)
library(psych)
library(corrplot)
```

```{r data files}
ds <- read_rds("../Newest Data/FIntv_2017_Comprehensive_withY1SpGradeData_withSYFUSNoT7_Cleaned_Demogs_6Nov2018.rds")

ds %<>% filter(!is.na(cd_purp_sc))
```

```{r custom functions}
alphatize <- function(data, vector){
  temp <- 
    data %>% 
    select(!!!vector) %>% # note that variables in ... must be pre-quoted using quos() function
    na.omit() %>% 
    psych::alpha() 
  
  temp$total$raw_alpha %>% broman::myround(2)
  # Example: 
  # var_list <- quos(disp, wt, cyl)
  # new_alpha <- alphatize(mtcars, var_list)
}

alphatize_full <- function(data, vector){
    data %>% 
    select(!!!vector) %>% # note that variables in ... must be pre-quoted using quos() function
    na.omit() %>% 
    psych::alpha() 
}

cv_compute <- function(data, cv_name, cv_vector){
  cv_name <- enquo(cv_name)
  data %>% 
      rowwise() %>% 
      mutate(!!quo_name(cv_name) := mean(c(!!!cv_vector), na.rm = TRUE)) %>% 
      ungroup()
}

factor_analysis <- function(data, vector){

  fact <- data %>% select(!!!vector)
  

 

  corr_table <- round(cor(fact, use = "pairwise.complete.obs"), digits = 3) # you need to determine how NAs should be treated. SPSS uses deleting NAs pairwise as a default, so R should do the same in order to compare the results

 ?cor

  corrplot(corr_table, method = "circle") # plot matrix

  #scree_plot <- fa.parallel(corr_table, fm = "pa", fa = "fa", main = "Scree Plot"); scree_plot

  scree_plot <- scree(corr_table, factors = TRUE, pc = FALSE, main = "Scree plot", hline = NULL, add = FALSE); scree_plot # pc: principal components, pc is used in Confirmatory Factor Analysis (CFA), instead of Exploratory Factor Analysis (EFA)

  # if the Eigen value is above the cutoff in the scree_plot, then you have a factor!

 

  # Begin Factor Analysis

  # dim(fact); str(fact)

 

  # when reviewing the output of factanal, the Factor of each item should be > .6 to consider these items as part of the composite that we want to compute.

  factanal(na.omit(fact),

    factors = 1, # how many factors to calculate

   rotation = "varimax") # "varimax" uncorrelate the items by computing an orthogonal vector with all the items

}

table.describe <- function(data, vector){
  data %>% select(!!!vector) %>% describe %>% round(., digits = 2) %>% kable(format = "html") %>% 
    kable_styling(bootstrap_options = c("hover", "responsive"), font_size = 12, full_width = F)
}

corr_table <- function(df, vars){
  df %>% # then
  select(!!!vars) %>%
  corstarsl.all() %>% 
  rownames_to_column(., var = "var") %>% 
  slice(-1) %>% 
  kable(format = "html") %>% 
  kable_styling(bootstrap_options = c("hover", "responsive"), font_size = 12, full_width = F)
}

corstarsl.all <- function(x){ 
require(Hmisc) 
x <- as.matrix(x) 
R <- rcorr(x)$r 
p <- rcorr(x)$P
n <- rcorr(x)$n

## define notions for significance levels; spacing is important.
mystars <- ifelse(p < .001, " ***", 
                  ifelse(p < .01, " **", 
                         ifelse(p < .05, " *", # significant
                                ifelse(p < 0.1, " †", # marginal
                                       ifelse(p < 0.15, " .", " "))))) # trending

## trunctuate the matrix that holds the correlations to two decimal
R <- format(round(cbind(rep(-1.11, ncol(x)), R), 3))[,-1] 

## add number of observations in parenthesis
n.p <- n %>% as.data.frame() %>% 
  mutate_all(funs(paste0("(", . ,")"))) %>% 
  as.matrix()

## build a new matrix that includes the correlations with their apropriate stars 
Rnew <- matrix(paste(R, mystars, n.p, sep=" "), ncol=ncol(x)) 
diag(Rnew) <- paste(diag(R), " ", sep="") 
rownames(Rnew) <- colnames(x) 
colnames(Rnew) <- paste(colnames(x), "", sep="") 

## remove upper triangle
Rnew <- as.matrix(Rnew)
Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
Rnew <- as.data.frame(Rnew) 

## remove last column and return the matrix (which is now a data frame)
Rnew <- cbind(Rnew[1:length(Rnew)-1])
return(Rnew) 
}
```

```{r raincloud plots}
n_obs <- function(x) sum(!is.na(x))
mn <- function(x) round(mean(x, na.rm = TRUE), 2)
mdn <- function(x) median(x, na.rm = TRUE)
std <- function(x) round(sd(x, na.rm = TRUE), 2)
lb <- function(x) round(mean(x, na.rm = TRUE) - sd(x, na.rm = TRUE), 2)
ub <- function(x) round(mean(x, na.rm = TRUE) + sd(x, na.rm = TRUE), 2)

sum_stats_round_new <- function(data, factors, variables) {
  ftr <- enquo(factors)
  var <- enquo(variables)
  
  data %>% 
    group_by(!!!ftr) %>% 
    summarise(
      n = n_obs(!!!var),
      mean = mn(!!!var),
      median = mdn(!!!var),
      sd = std(!!!var),
      lower = lb(!!!var),
      upper = ub(!!!var))
}

geom_flat_violin <-
  function(mapping = NULL,
           data = NULL,
           stat = "ydensity",
           position = "dodge",
           trim = TRUE,
           scale = "area",
           show.legend = NA,
           inherit.aes = TRUE,
           ...) {
    ggplot2::layer(
      data = data,
      mapping = mapping,
      stat = stat,
      geom = GeomFlatViolin,
      position = position,
      show.legend = show.legend,
      inherit.aes = inherit.aes,
      params = list(trim = trim,
                    scale = scale,
                    ...)
    )
  }

GeomFlatViolin <-
  ggproto(
    "GeomFlatViolin",
    Geom,
    setup_data = function(data, params) {
      data$width <- data$width %||%
        params$width %||% (resolution(data$x, FALSE) * 0.9)
      
      # ymin, ymax, xmin, and xmax define the bounding rectangle for each group
      data %>%
        dplyr::group_by(.data = ., group) %>%
        dplyr::mutate(
          .data = .,
          ymin = min(y),
          ymax = max(y),
          xmin = x,
          xmax = x + width / 2
        )
    },
    
    draw_group = function(data, panel_scales, coord)
    {
      # Find the points for the line to go all the way around
      data <- base::transform(data,
                              xminv = x,
                              xmaxv = x + violinwidth * (xmax - x))
      
      # Make sure it's sorted properly to draw the outline
      newdata <-
        base::rbind(
          dplyr::arrange(.data = base::transform(data, x = xminv), y),
          dplyr::arrange(.data = base::transform(data, x = xmaxv), -y)
        )
      
      # Close the polygon: set first and last point the same
      # Needed for coord_polar and such
      newdata <- rbind(newdata, newdata[1,])
      
      ggplot2:::ggname("geom_flat_violin",
                       GeomPolygon$draw_panel(newdata, panel_scales, coord))
    },
    
    draw_key = draw_key_polygon,
    
    default_aes = ggplot2::aes(
      weight = 1,
      colour = "grey20",
      fill = "white",
      size = 0.5,
      alpha = NA,
      linetype = "solid"
    ),
    
    required_aes = c("x", "y")
  )
```
## Well-being

### Eudaimonic Well-being
#### Summarizing items
```{r}
vector_purpose <- quos(purpose_meaning, purpose_contribute)

table.describe(ds, vector_purpose)
```

#### Correlational analysis

```{r}
corr_table(ds, vector_purpose)
```

#### Compute and review Eudaimonic Well-being Composite
```{r}
ds %<>% cv_compute(cv_name = purpose_comp2, cv_vector = vector_purpose)
```

```{r}
hist(ds$purpose_comp2)
boxplot(ds$purpose_comp2)
```

| Eudaimonic wellbeing (purpose_comp2) | |
|:---------------------|:--------------------------------------------------------------------------------------|
| Scale | 1 = Not at all ... 5 = A great deal |
| Items | 1.      Right now, how much do you feel that your life has a sense of direction or meaning to it? |
|       | 2.      Right now, how much do you feel that you have something to contribute to society? |


### Happiness

```{r}
ds %<>% 
  mutate(happy_unhappy_r_use_this = 8 - happy_unhappy_r)
```

#### Summarizing items
```{r}
vector_happy <- quos(happy_person, happy_comppeer, happy_enjoylife, happy_unhappy_r_use_this)

table.describe(ds, vector_happy)
```

#### Reliability analysis

```{r}
alpha_happy <- alphatize(ds, vector_happy) # Alpha: 0.88

alphatize_full(ds, vector_happy)

corr_table(ds, vector_happy)
```

#### Factor analysis
```{r}
factor_analysis(ds, vector_happy) ##Items 4 and 6 don't fit. 
```

#### Compute and review Happiness Composite
```{r}
ds %<>% cv_compute(cv_name = happy_comp4, cv_vector = vector_happy)
```

```{r}
hist(ds$happy_comp4) # fairly normally distributed.
boxplot(ds$happy_comp4)
```

| Happiness (happy_comp4) | ${\alpha}$ = `r alpha_happy`|
|:---------------------|:--------------------------------------------------------------------------------------|
| Scale | 1 = Not a very happy person/Less happy/Not at all ... 7 = A very happy person/More happy/A great deal |
| Items | 1.      In general, I consider myself: |
|       | 2.      Compared with most of my peers, I consider myself: |
|       | 3.      Some people are generally very happy. They enjoy life regardless of what is going on, getting the most out of everything. To what extent does this characterization describe you? |
|       | 4.      Some people are generally not very happy. Although they are not depressed, they never seem as happy as they might be. To what extent does this characterization describe you? (reversed) |



## Health
### Overall Physical Health

```{r}
ds %<>% 
  mutate(
    health_sickeasier_r = health_health_sickeasierR,
    health_worse_r = health_health_worse_r,
    health_healthyanybody = health_health_healthyanybody,
    health_excellent = health_health_excellent,
    health_sickeasier_r_use_this = 6 - health_sickeasier_r,
    health_worse_r_use_this = 6 - health_worse_r)
```

#### Summarizing items
```{r}
vector_healthmosoverall <- quos(health_overall, health_sickeasier_r_use_this, health_healthyanybody, health_worse_r_use_this, health_excellent)

table.describe(ds, vector_healthmosoverall)
```

#### Reliability analysis

```{r}
alpha_healthmosoverall <- alphatize(ds, vector_healthmosoverall) # Alpha: 0.77

alphatize_full(ds, vector_healthmosoverall)

corr_table(ds, vector_healthmosoverall)

health <- ds %>% filter(startedSYFUS == 1) %>%  select(starts_with("health"))
rm(health)
```

#### Factor analysis
```{r}
factor_analysis(ds, vector_healthmosoverall)
```

#### Compute and review Overall Physical Health Composite
```{r}
ds %<>% cv_compute(cv_name = healthmosoverall_comp5, cv_vector = vector_healthmosoverall)
```

```{r}
hist(ds$healthmosoverall_comp5)
boxplot(ds$healthmosoverall_comp5)
```

| Overall Physical Health (healthmosoverall_comp5) | ${\alpha}$ = `r alpha_healthmosoverall`|
|:---------------------|:--------------------------------------------------------------------------------------|
| Scale | 1 = Poor/Definitely false ... 5 = Excellent/Definitely true | 
| Items | 1. In general, would you say your health is:  |
|       | 2.      I seem to get sick a little easier than other people. (reversed) |
|       | 3.      I am as healthy as anybody I know. |
|       | 4.      I expect my health to get worse. (reversed) |
|       | 5.      My health is excellent. | 

### Perceived Stress Scale (Secondary Appraisal)

```{r}
ds %<>% 
  mutate(pss_handle_r_use_this = 6- pss_handle_r,
         pss_yourway_r_use_this = 6 - pss_yourway_r)
```

#### Summarizing items
```{r}
vector_pss <- quos(pss_unable, pss_handle_r_use_this, pss_yourway_r_use_this, pss_difficulties)

table.describe(ds, vector_pss)
```

#### Reliability analysis

```{r}
alpha_pss <- alphatize(ds, vector_pss)

alphatize_full(ds, vector_pss)

corr_table(ds, vector_pss)
```

#### Factor analysis
```{r}
factor_analysis(ds, vector_pss) ##Items 4 and 6 don't fit. 
```

#### Compute and review PSS Composite
```{r}
ds %<>% cv_compute(cv_name = pss_comp4, cv_vector = vector_pss)
```

```{r}
hist(ds$pss_comp4)
boxplot(ds$pss_comp4)
```

| Perceived stress scale (pss_comp4) | ${\alpha}$ = `r alpha_pss`|
|:---------------------|:--------------------------------------------------------------------------------------|
| Scale | 1 = Never ... 5 = Very often |
| Items | 1.      In the last month of school, how often have you felt that you were unable to control the important things in your life? |
|       | 2.      In the last month of school, how often have you felt confident about your ability to handle your personal problems? (reversed) |
|       | 3.      In the last month of school, how often have you felt that things were going your way? (reversed) |
|       | 4.      In the last month of school, how often have you felt difficulties were piling up so high that you could not overcome them? |

### Overall Mental Health

```{r}
ds %<>% 
  mutate(
    screener_anxnervous = screener_screener_anxnervous,
    screener_anxworry = screener_screener_anxworry,
    screener_deplittleinterest = screener_screener_dep_littleinterest,
    screener_dephopeless = screener_screener_dephopelessness,
    screener_anxnervous_new_scale = screener_anxnervous - 1,
    screener_anxworry_new_scale = screener_anxworry - 1,
    screener_deplittleinterest_new_scale = screener_deplittleinterest - 1,
    screener_dephopeless_new_scale = screener_dephopeless - 1,
    screener_anxnervous_new_scale_r = 4 - screener_anxnervous,
    screener_anxworry_new_scale_r = 4 - screener_anxworry,
    screener_deplittleinterest_new_scale_r = 4 - screener_deplittleinterest,
    screener_dephopeless_new_scale_r = 4 - screener_dephopeless,
    mhealthgeneral_z = scale(mhealth_general),
    screener_anxnervous_new_scale_r_z = scale(screener_anxnervous_new_scale_r),
    screener_anxworry_new_scale_r_z = scale(screener_anxworry_new_scale_r),
    screener_deplittleinterest_new_scale_r_z = scale(screener_deplittleinterest_new_scale_r),
    screener_dephopeless_new_scale_r_z = scale(screener_dephopeless_new_scale_r))
```

#### Summarizing items
```{r}
vector_overallmentalhealth_nz <- quos(mhealth_general, screener_anxnervous_new_scale_r,
    screener_anxworry_new_scale_r,
    screener_deplittleinterest_new_scale_r,
    screener_dephopeless_new_scale_r)

table.describe(ds, vector_overallmentalhealth_nz)

vector_overallmentalhealth <- quos(mhealthgeneral_z, screener_anxnervous_new_scale_r_z, screener_anxworry_new_scale_r_z, screener_deplittleinterest_new_scale_r_z, screener_dephopeless_new_scale_r_z)

table.describe(ds, vector_overallmentalhealth)
```

#### Reliability analysis
```{r}
alpha_overallmentalhealth <- alphatize(ds, vector_overallmentalhealth) # Alpha: 0.89

alphatize_full(ds, vector_overallmentalhealth)

corr_table(ds, vector_overallmentalhealth)
```

#### Factor analysis
```{r}
factor_analysis(ds, vector_overallmentalhealth)
```

#### Compute and review Overall Mental Health Composite
```{r}
ds %<>% cv_compute(cv_name = overallmentalhealth_comp5_z, cv_vector = vector_overallmentalhealth)
```

```{r}
hist(ds$overallmentalhealth_comp5_z)
boxplot(ds$overallmentalhealth_comp5_z)
```

| Overall Mental Health (overallmentalhealth_comp5_z) | ${\alpha}$ = `r alpha_overallmentalhealth`|
|:---------------------|:--------------------------------------------------------------------------------------|
| Scale | Standardized (z-scored) | 
| Scale | 1 = Poor ... 5 = Excellent | 
| Item  | 1. In general, would you say your mental health is: |
| Scale | 0 = Not at all ... 3 = Nearly every day | 
|       | Over the last 2 weeks, how often have you been bothered by the following problems? |
| Items | 2.      Feeling nervous, anxious, or on edge. (reversed) |
|       | 3.      Not being able to stop or control worrying. (reversed) |
|       | 4.      Little interest or pleasure in doing things. (reversed) |
|       | 5.      Feeling down, depressed, or hopeless. (reversed) | 
Note: First, I reverse coded items 2 to 5. Then, I standardized each individual item. And finally, I averaged all of them together.
